A thesis draft

### 2018-11-21 res/sections/09-RelatedWork.tex
Add some other works

@@

Compared to our solution, these implementations does not present an unified
framework that gives the possbility orchestrate different network slices
consistently. Adopting Kubernetes gives the advantage to use the Kubernetes
Federation feature~\cite{kubeFederation}, enabling the possibility to simplify
the management of multiple network slice in end-to-end services.

@@

Another important aspect related to 5G networking and network slice is the one
regarding security. Security in this context plays a fundamental role, since
secure communications depends on the security of the overall system.
In~\cite{kotulski2017end} the authors carry out a deep analysis about the
network slice security, putting an emphasis on how this new element (the network
slice) brings additional security questions and problems, especially about
isolation. Moreover, slicing in 5G introduces the concept of shared services,
that is contrary with the definition of isolation itself. In particular,
resource isolation gives the possibility to avoid attacks such us slice
resources exhaustion. Additionally, the authors give a critic regarding the ETSI
NFV-MANO standard making too general assumptions regarding the whole system.
Finally, a Service-Level Agreement (SLA) based orchestration criteria between
network slices is proposed as a viable solution to solve the security problems
about isolation. We tried to mitigate the security consern presented above using
the integrated Role Base Access Control system (RBAC) and other security policy
bundled in by default in Kubernetes.

\section{Provision capabilities}
We noted how, in some other NFV/ETSI-MANO proposals like~\cite{soares2015toward}
and~\cite{abujoda2015midas}, the implementations relays on a static provision
system, where the SFC paths are somehow defined at deploy time, and can't change
without decomissioning, editing and deploying the chain again. Our proposal,
instead, is able to support chain editing on-the-fly, allowing NFV to dynamically
change SFP.

@@

\subsection{Other SFC implementation}
Since the SFC technology was proposed many work came out proposing different implementation solutions. In this part there is an overview of some of them.

In~\cite{GhaznaviSAB16} proposed optimization model to calculate the optimal
location of VNFs based on different metrics such as bandwidth, load balancing
and routes. This decomposes SFC on performance requirements eliminating the
throughput bound of a chain to a single VNF or a single physical machine.
Mathematical models developed was tested in a simulation enviroment. A critical
enhancement to this work could be to test algorithm in a real environment, under
different conditions of traffic load: if it efficiant even in this senario it
can be useful to the orchestration and management part of the ecosystem because
it can reduce resource waste.

@@

Another noteworthy work is~\cite{xia2015optical} that discuss the packet
delivery through function chaining in high capacity network exploiting aggregate
flow steering. The architecture proposed make use of SDN and cloud platform to
deploy VMs on which run VNFs assuming that the SDN and network element are
connected using optical circuit switching, taking advantage of Wave Selective
Switchig (WSS), to route (switch) signals between optical fibres on a
per-wavelength basis. Thank to the implementation of the SDN controller and the
communication between the previous element and the VNFM, this architecture is
able to provide good capabilities in terms of flexibilities. Another element
that helps the flexibility is the high performance link: in this way they get
rid of problems in terms of connection time and bandwidth. However, in the paper
authors assumes really specific hardware in that underlying infrastructure that
connects the overall system: this is not suitable to be deployed in a general
purpose infrastructure or using IaaS. It will be interesting to evaluated the
same work on different instrumentation. A clashing aspect is the time to make a
VM up and running compared to times of servvice chaining configuration/packet
delivery. Using containers the instantiation of virtual functions should employ
less time.

A rilevant work on function chaining in network is~\cite{trajkovska2017sdn}. In
this work author efforts are concentrated on joining SDN and VNF technologies to
create SFCs. They developed an SDN-driven SDK, a virtual traffic classifier to
analyze traffic in real-time and decide the optimal chain for it and a VNF
specialized on video transdecoding, used event to evaluate the performances of
the whole system. Chaining is performed exploiting layer 2 connectivity,
using OpenvSwitch as virtual network svitches an OpenDayLight in order to
route the traffic on a set of policies. However the solution does not provide
any mechanism to automatic deployment of chains and services: this can be an
issue in particular in case of VNF fault. Orchestration and some mechanisms of
fault tollerance are critical in particular in a real environment, enabling
autoscaling on user demand or traffic load. Automated deployment also make
possible the recreation of a virtual machine in case of fault. As a matter of
fact that a virtual function can fail depending on an erroneus load balancing
policy or too heavy computational load and it is critical in order to do not
interrupt end-to-end communication to bring up the VNF as soon as possible. This
recreation process can be slow due to the usage of VMs to deploy the
functions, that could take minutes to startup.

>>>>

One of the first proposal that take advantage of container in to take on network
edges NFV is~\cite{cziva2017container}. The authors present the work, based on
previous definition of the platform defined in~\cite{cziva2015container} to
orchestrate the virtual function and to deploy it as close as possible to the
data sender to classify traffic and choose the appropriate functions
immediately.

@@

Compared to our solution, these implementations does not present an unified
framework that gives the possibility orchestrate different network slices
consistently. Adopting Kubernetes gives the advantage to use the Kubernetes
Federation feature~\cite{kubeFederation}, enabling the possibility to simplify
the management of multiple network slice in end-to-end services.

@@

Another important aspect related to 5G networking and network slice is the one
regarding security. Security in this context plays a fundamental role, since
secure communications depends on the security of the overall system.
In~\cite{kotulski2017end} the authors carry out a deep analysis about the
network slice security, putting an emphasis on how this new element (the network
slice) brings additional security questions and problems, especially about
isolation. Moreover, slicing in 5G introduces the concept of shared services,
that is contrary with the definition of isolation itself. In particular,
resource isolation gives the possibility to avoid attacks such us slice
resources exhaustion. Additionally, the authors give a critic regarding the ETSI
NFV-MANO standard making too general assumptions regarding the whole system.
Finally, a Service-Level Agreement (SLA) based orchestration criteria between
network slices is proposed as a viable solution to solve the security problems
about isolation. We tried to mitigate the security concern presented above using
the integrated Role Base Access Control system (RBAC) and other security policy
bundled in by default in Kubernetes.

\section{Provision capabilities}
We noted how, in some other NFV/ETSI-MANO proposals like~\cite{soares2015toward}
and~\cite{abujoda2015midas}, the implementations relays on a static provision
system, where the SFC paths are somehow defined at deploy time, and can't change
without decommissioning, editing and deploying the chain again. Our proposal,
instead, is able to support chain editing on-the-fly, allowing NFV to
dynamically change SFP.

@@

\subsection{SFC implementation}
Since the SFC technology was proposed many work came out proposing different
implementation solutions. In this part there is an overview of some of them.

In~\cite{GhaznaviSAB16} proposed optimization model to calculate the optimal
location of VNFs based on different metrics such as bandwidth, load balancing
and routes. This decomposes SFC on performance requirements eliminating the
throughput bound of a chain to a single VNF or a single physical machine.
Mathematical models developed was tested in a simulation environment. A critical
enhancement to this work could be to test algorithm in a real environment, under
different conditions of traffic load: if it efficient even in this scenario it
can be useful to the orchestration and management part of the ecosystem because
it can reduce resource waste.

@@

Another noteworthy work is~\cite{xia2015optical} that discuss the packet
delivery through function chaining in high capacity network exploiting aggregate
flow steering. The architecture proposed make use of SDN and cloud platform to
deploy VMs on which run VNFs assuming that the SDN and network element are
connected using optical circuit switching, taking advantage of Wave Selective
Switching (WSS), to route (switch) signals between optical fibers on a
per-wavelength basis. Thank to the implementation of the SDN controller and the
communication between the previous element and the VNFM, this architecture is
able to provide good capabilities in terms of flexibility. Another element
that helps the flexibility is the high performance link: in this way they get
rid of problems in terms of connection time and bandwidth. However, in the paper
authors assumes really specific hardware in that underlying infrastructure that
connects the overall system: this is not suitable to be deployed in a general
purpose infrastructure or using IaaS. It will be interesting to evaluated the
same work on different instrumentation. A clashing aspect is the time to make a
VM up and running compared to times of service chaining configuration/packet
delivery. Using containers the instantiation of virtual functions should employ
less time.

A relevant work on function chaining in network is~\cite{trajkovska2017sdn}. In
this work author efforts are concentrated on joining SDN and VNF technologies to
create SFCs. They developed an SDN-driven SDK, a virtual traffic classifier to
analyze traffic in real-time and decide the optimal chain for it and a VNF
specialized on video transdecoding, used event to evaluate the performances of
the whole system. Chaining is performed exploiting layer 2 connectivity,
using OpenvSwitch as virtual network switches an OpenDayLight in order to
route the traffic on a set of policies. However the solution does not provide
any mechanism to automatic deployment of chains and services: this can be an
issue in particular in case of VNF fault. Orchestration and some mechanisms of
fault tolerance are critical in particular in a real environment, enabling
autoscaling on user demand or traffic load. Automated deployment also make
possible the recreation of a virtual machine in case of fault. As a matter of
fact that a virtual function can fail depending on an erroneous load balancing
policy or too heavy computational load and it is critical in order to do not
interrupt end-to-end communication to bring up the VNF as soon as possible. This
recreation process can be slow due to the usage of VMs to deploy the
functions, that could take minutes to startup.
